Untitled

### 2024-10-03 analysis/paper/access-ice.qmd
Uses pdf

---
title: "Untitled"
format: html
execute: 
  echo: false
  warning: false
  message: false
filters:
  - ../../_extensions/pandoc-ext/abstract-section/abstract-section.lua
  - ../../_extensions/mloubout/critic-markup/critic-markup.lua
---

>>>>

---
title: "Untitled"
format: pdf
execute: 
  echo: false
  warning: false
  message: false
filters:
  - ../../_extensions/pandoc-ext/abstract-section/abstract-section.lua
  - ../../_extensions/mloubout/critic-markup/critic-markup.lua
---
